MCLM parameters, interactive example

### 2024-05-20 apps/Graphical_representation_interactive.qmd
Adds y-axis breaks in transformed latent space

  lt_sample_transf() |> ggplot(aes(x = theta_1, y = theta_2)) +
    geom_vline(xintercept = 0, linewidth = LINE_WIDTH) +
    geom_abline( # Oblique `theta_2` axis
      intercept = 0,
      slope     = tan_vec_1,
      linewidth = LINE_WIDTH
    ) +
    geom_abline( # Oblique panel grid lines
      intercept = -3:3 * basis_vec_2[2],
      slope     = tan_vec_1,
      linewidth = LINE_WIDTH,
      linetype  = "C6"
    ) +
    geom_point(alpha = .5) +
    scale_x_continuous(
      limits       = c(-3, 3),
      breaks       = -3:3,
      minor_breaks = NULL,
      name         = NULL,
      oob          = oob_keep
    ) +
    scale_y_continuous(
      limits       = c(-3, 3),
      breaks       = -3:3,
      name         = NULL,
      oob          = oob_keep
    ) +
    coord_fixed(expand = FALSE, clip = "on") +
    theme(
      axis.line          = element_blank(),
      panel.grid.major.x = element_line(
        color     = "black",
        linewidth = LINE_WIDTH,
        linetype  = "C6"
     )
    )
})
output$ts_transformed <- renderPlot({
})
```

>>>>

  lt_sample_transf() |> ggplot(aes(x = theta_1, y = theta_2)) +
    geom_vline(xintercept = 0, linewidth = LINE_WIDTH) +
    geom_abline( # Oblique `theta_2` axis
      intercept = 0,
      slope     = tan_vec_1,
      linewidth = LINE_WIDTH
    ) +
    geom_abline( # Oblique panel grid lines
      intercept = -3:3 * basis_vec_2[2],
      slope     = tan_vec_1,
      linewidth = LINE_WIDTH,
      linetype  = "C6"
    ) +
    geom_point(alpha = .5) +
    scale_x_continuous(
      limits       = c(-3, 3),
      breaks       = -3:3,
      minor_breaks = NULL,
      name         = NULL,
      oob          = oob_keep
    ) +
    scale_y_continuous(
      limits       = c(-3, 3),
      breaks       = -3:3 * basis_vec_2[2] -3 * basis_vec_1[2],
      labels       = -3:3,
      name         = NULL,
      oob          = oob_keep
    ) +
    coord_fixed(expand = FALSE, clip = "on") +
    theme(
      axis.line          = element_blank(),
      panel.grid.major.x = element_line(
        color     = "black",
        linewidth = LINE_WIDTH,
        linetype  = "C6"
     )
    )
})
output$ts_transformed <- renderPlot({
})
```
